---
title: "DG MARE"
author: "Laurence Kell and Niels Hintzen"
date:   5th to 6th December 2016; Brussels
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo=FALSE}
library(knitr)

opts_chunk$set(comment=NA, 
               warning=FALSE, 
               message=FALSE, 
               error  =FALSE, 
               echo   =FALSE, 
               eval   =TRUE,
               fig.width =7, 
               fig.height=3)
```


## Outline

An introduction to the current state of the art in Quantitative Fisheries Science as applied by the scientific bodies of the Regional Fisheries Management Organisations (RFMOs), with emphasis on the tuna RFMOs.

The course covers current practice in stock assessment and provision of advice. It also covers the evaluation through simulation of alternative management plans. Presentions will be based on recent examples.

## Learning goals

To 

+ Understand the basic ideas behind the models used to provide advice.
+ Identify the relative advantages and limitations of alternative stock assessment models.
+ Perceive the difficulties in parameter estimation common to all fisheries models and the effect this uncertainty has on the robustness of advice.
+ Provide an introduction to Management Strategy Evaluation and the it requires in management advice frameworks.
+ Be better equipped for a constructive dialogue between managers, scientists and stakeholders on how Quantitative Fisheries Science can help managing fishery systems.

## Organisation

The different models and approaches, and the ideas behind them, are introduced and explained, focusing on

+ Data requirements
+ Assumptions
+ Limitations
+ Interpretation of results

Example are runs and the results analysed and dissected, with examples taken from recent scientific outputs of different RFMOs.

## Participants

Around 10-15  DG MARE staff with involvement in scientific activities in RFMOs. They are familiar with scientific work ongoing In RFMOs but most of them have not been involved in hands-on work for several (lasts) years. They should not be expected to run analysis themselves, but access to relevant software and source code will be given for those willing to replicate and explore them in their own time. The course should be open to other DG MARE staff with scientific interests outside RFMOs.

\newpage
## Agenda
| Day 1         |                                                         |
| --------------|---------------------------------------------------------|
| 09:30 – 10:15 | **Presentation:** The Kobe advice framework             |
| 10:15 – 10:45 | **Presentation:** Assessment, data needs and assumptions|
| 10:45 – 11:00 | **Tea Break:**                                          |
| 11:00 – 12:15 | **Exercise:**                                           |
| 12:15 – 13:15 | **Lunch:**                                              |
| 13:15 – 14:30 | **Presentation:** Assessment, data needs and assumptions|
| 14:30 – 15:15 | **Exercise:**                                           |
| 15:15 – 15:30 | **Tea Break:**                                          |
| 15:30 – 16:30 | **Presentation:** Stock Status and Reference points     |
| 16:30 – 17:00 | **Summary of the day:** questions and answers           |

| Day 2         |                                                       |
| --------------|-------------------------------------------------------|
| 09:00 – 10:15 | **Presentation:** Projection scenarios  $~~~~~~~~~~~~~~~~~~~~~~~~$|
| 10:15 – 10:45 | **Exercise:**                                         |
| 10:45 – 11:00 | **Tea Break:**                                        |
| 11:00 – 12:15 | **Presentation:** Management Plans                    |
| 12:15 – 13:15 | **Lunch:**                                            |
| 13:15 – 14:00 | **Exercise:**                                         |
| 14:00 – 16:00 | **Summary of the day:** questions and answers         |

