---
title: "Management Strategy Evaluation"
subtitle: "An Example"
author: "Laurence Kell"
output: ioslides_presentation
---


```{r knitr, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(knitr)

opts_chunk$set(comment=NA, 
               warning=FALSE, 
               message=FALSE, 
               error  =FALSE, 
               echo   =FALSE, 
               fig.width =8, 
               fig.height=5,
               fig.path  ="../tex/mse-",
               cache     =TRUE)

iFig=0
iTab=0
```

```{r libload}
library(mpb)
library(FLBRP)
library(kobe)

load("/home/laurie/Desktop/flr/tutorials/advice_framework/data/eql.RData")
```

```{r conditioning, echo=FALSE}
eql      =eqlScen[[1]]
fbar(eql)=c(seq(0,1.5,length.out=51),rep(1.5,50))*refpts(eql)["msy","harvest"]

om       =mpb:::FLStock2biodyn(fwd(eql))
params(om)["b0"]=1
om=propagate(mpb:::fwd(om,catch=catch(om)),100)

mp=om

set.seed(1234)

pe=rlnorm(100,FLQuant(0,dimnames=list(year=1:101)),.2)

source('~/Desktop/flr/mpb/R/biodyn-mse.R')

res=demo(om,mp,pe,start=50,end=90,silent=TRUE)
```

## Comparison of Operating Model and Management Procedure

```{r om-mp}
plot(res)+
  scale_x_continuous(limits=c(1,80))+
  theme_bw()
```

## Kobe Phase Plot

```{r kobe}
kobePhase(subset(kobe(res[[1]]),year%in%60:80))+
  geom_point(aes(stock,harvest,col=year))+
  geom_point(aes(stock,harvest),shape=21,fill="black",col=NA)
```

## Kobe Phase Plot

```{r kobe-mar}
kobe:::kobePhaseMar2(subset(kobe(res[[1]]),year%in%60:80)[c("stock","harvest")])
```

## Operating Model Time Series

```{r om}
plot(res[[1]])+
 geom_hline(aes(yintercept=X1),col="orange",
            data=cbind(qname=c("Yield","Harvest","Stock"),data.frame(iter(refpts(om),1))))+
 geom_line(aes(year,data,group=iter),col="grey",
             data=transform(ldply(FLQuants(res[[1]],
                          "Stock"=stock,
                          "Harvest"=harvest,
                          "Yield"=catch),function(x) 
                                      as.data.frame(iter(x, 1:3),drop=TRUE)),
                          qname=.id))+
  theme_bw()+scale_x_continuous(limits=c(1,80))
```


## Operating Model Summary Statistics

Statistics should be independent, i.e. not overlapping so that the trade-offs between management objectives are clear, for eaxmple

+ Safety
+ Yield
+ Stability

## Operating Model Summary Statistics
### Safety

#### Probability of being in a Kobe Quadrant
```{r safety}
safe=kobe:::smry(kobe(res[[1]])[,c("stock","harvest")])

rownames(safe)=""

names(safe)[3:5]=c("Red","Yellow","Green")
round(safe[c("Red","Green","Yellow")],2)
```

#### Probability of 

```{r safety2}
names(safe)[6:7]=c("Over Fished","Over Fishing")
round(safe[c("Over Fished","Over Fishing")],2)
```


## Operating Model Summary Statistics

### Yield

Average Yield as a ratio of $MSY$
```{r yield}
round(mean(c(as.FLQuant(adply(harvest(window(res[[1]],start=60,end=80)),6,function(x) data.frame(data=mean(x))))))/mean(c(refpts(om)["fmsy"])),2)
```

Average Effort as a ratio of Effort at $F_{MSY}$
```{r yield2}
round(mean(c(as.FLQuant(adply(catch(  window(res[[1]],start=60,end=80)),6,function(x) data.frame(data=mean(x))))))/mean(c(refpts(om)["msy"])),2)
```

## Operating Model Summary Statistics

### Stability
Average Annual Variability in

+ Stock 6%
+ F     20%
+ Yield 21%


```{r stability, eval=FALSE}
paste("Stock: ", round(mean(c(aav(stock(  window(res[[1]],start=60,end=80))))),2)*100, " %", sep="")
paste("F    : ",round(mean(c(aav(harvest(window(res[[1]],start=60,end=80))))),2)*100, " %", sep="")
paste("Yield: ", round(mean(c(aav(catch(  window(res[[1]],start=60,end=80))))),2)*100, " %", sep="")
```

# References

<!-- pb=FLBRP(ple4) -->
<!-- pb=propagate(FLBRP(ple4),2,params=TRUE) -->
<!-- params(pb)["a"]=2 -->
<!-- pb=brp(pb) -->
<!-- plot(pb) -->

